Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex
spellcheck exp

Tab.~\ref{tab:who_initializations} gives the correponding results for
the various methods on a subset of the 3D Object Classes car
dataset~\cite{Savarese07} (all images corresponding to one particular
car instance, seen from different viewpoints), reporting 3 quantities:
detection performance in average precision (AP), pose estimation in mean
precision in pose estimtation (MPPE), and the respective runtime.
%
For all methods, the table gives the results with and without
calibration, using the calibration method of~\cite{Aubry14}. This
calibration learns affine transformation of the detection confidence.
For each method, we generated templates for 1 CAD model exemplar
rendered from 24 azimuth and 4 elevation angles.
% Since WHO variants uses HOG features, they are slower than
% HOG templates but WHO variants in general performs better than WHO by
% significant margin. However, WHO using Cholesky decomposition with
% Gaussian Elemination takes the most time yet performs worse than
% NZ-WHO which is two order of magnitude faster to generate.

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensiv, resulting in runtimes that are two orders of
magnitudes larger than without calibration. Strikinly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

@@

\subsection{2D-3D Matching as an Object Detector} 
\label{sec:exp_iso}
In this section, we evaluate the performance of our method in
isolation, for the task of object class detection and viewpoint
estimation, on the 3D Object Classes datset~\cite{Savarese07}, for the
categories {\em car} and {\em bicycle}.

To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
using $9$ different CAD models and a total of \scream{} different
viewpoints, using $X$ different evelation angles, $X$ azimuth angles,
and $X$ focal lengths. We run the entire ensemble exhaustively over
each test image, in a sliding window fashion.

@@

To show such ability, we evaluat our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

@@

\paragraph{Robustness.}
% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections, 
While the R-CNN detector~\cite{Girshick14} is highly robust to
variations in object appearance and even occlusion and truncation,
the resulting bounding box detections vary largely in the object
portions that they contain, which provides a major challenge to any
method that uses these detections as an input for further processing,
such as ours.
%
In order to accomodate this variability, we add a considerable context
region around the proposed bounding boxes before running our method.
We assume that the object can be arbitrarily truncated by the bounding
box and search all plausible scales and translations. This can be
efficiently computed using FFT-based convolution
(Section. \ref{sec:fft}).

@@

\begin{figure}[h]
\setlength\tabcolsep{5pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
\end{tabular}
\caption{Robustness of our method for against irregular and truncated
  R-CNN detection proposals (cyan).}
  % \cite{Girshick14}. Blue box is the R-CNN detection that is feed into
  % the system as initial detection. Purple box and overlaid rendering
  % is the final output of the system. Note that for various overlapping
  % bounding boxes, our system accurately estimated the reasonable
  % result}
  \label{fig:stability}
\end{figure}

>>>>

Tab.~\ref{tab:who_initializations} gives the corresponding results for
the various methods on a subset of the 3D Object Classes car
dataset~\cite{Savarese07} (all images corresponding to one particular
car instance, seen from different viewpoints), reporting 3 quantities:
detection performance in average precision (AP), pose estimation in mean
precision in pose estimation (MPPE), and the respective runtime.
%
For all methods, the table gives the results with and without
calibration, using the calibration method of~\cite{Aubry14}. This
calibration learns affine transformation of the detection confidence.
For each method, we generated templates for 1 CAD model exemplar
rendered from 24 azimuth and 4 elevation angles.
% Since WHO variants uses HOG features, they are slower than
% HOG templates but WHO variants in general performs better than WHO by
% significant margin. However, WHO using Cholesky decomposition with
% Gaussian Elemination takes the most time yet performs worse than
% NZ-WHO which is two order of magnitude faster to generate.

\paragraph{Results.}
In Tab.~\ref{tab:who_initializations}, we observe that, on average,
calibration indeed improves performance in terms of AP, sometimes
drastically (e.g., from $54.4$ to $92.8$ for WHO-CG-Z), as observed in
prior work~\cite{Aubry14}. At the same time, calibration is
computationally expensive, resulting in runtimes that are two orders of
magnitudes larger than without calibration. Strikingly, our method
NZ-WHO-CG achieves the second best AP of $90.0$ while completing in 79
ms vs. 8.7 s when using calibration.

@@

\subsection{2D-3D Matching as an Object Detector} 
\label{sec:exp_iso}
In this section, we evaluate the performance of our method in
isolation, for the task of object class detection and viewpoint
estimation, on the 3D Object Classes dataset~\cite{Savarese07}, for the
categories {\em car} and {\em bicycle}.

To that end, we create an ensemble of NZ-WHO templates (Sect.~\ref{})
using $9$ different CAD models and a total of \scream{} different
viewpoints, using $X$ different elevation angles, $X$ azimuth angles,
and $X$ focal lengths. We run the entire ensemble exhaustively over
each test image, in a sliding window fashion.

@@

To show such ability, we evaluate our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

@@

\paragraph{Robustness.}
% Generic object detectors give overlapping detection bounding boxes of the same object which can be handled by non maximal suppression. For these overlapping detections, 
While the R-CNN detector~\cite{Girshick14} is highly robust to
variations in object appearance and even occlusion and truncation,
the resulting bounding box detections vary largely in the object
portions that they contain, which provides a major challenge to any
method that uses these detections as an input for further processing,
such as ours.
%
In order to accommodate this variability, we add a considerable context
region around the proposed bounding boxes before running our method.
We assume that the object can be arbitrarily truncated by the bounding
box and search all plausible scales and translations. This can be
efficiently computed using FFT-based convolution
(Section. \ref{sec:fft}).

@@

\begin{figure}[h]
\setlength\tabcolsep{5pt}
\begin{tabular}{cc}
  \includegraphics[width=0.45\linewidth]{car_pascal/1.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/2.png} \\   
  \includegraphics[width=0.45\linewidth]{car_pascal/3.png} &   
  \includegraphics[width=0.45\linewidth]{car_pascal/4.png} \\   
\end{tabular}
\caption{Robustness of our method against irregular and truncated
  R-CNN detection proposals (cyan).}
  % \cite{Girshick14}. Blue box is the R-CNN detection that is feed into
  % the system as initial detection. Purple box and overlaid rendering
  % is the final output of the system. Note that for various overlapping
  % bounding boxes, our system accurately estimated the reasonable
  % result}
  \label{fig:stability}
\end{figure}
